\begin{frame}{Econ 57a, Environmental Economics, Fall 2019}
\protect\hypertarget{econ-57a-environmental-economics-fall-2019}{}

\begin{block}{QFT: the question formulation exercise}

\end{block}

\end{frame}

\begin{frame}{}
\protect\hypertarget{section}{}

Please sit with your group members for now

\end{frame}

\begin{frame}{Take two minutes}
\protect\hypertarget{take-two-minutes}{}

Give your group an awesome name!!

\end{frame}

\begin{frame}{The Question Formulation Exercise}
\protect\hypertarget{the-question-formulation-exercise}{}

\begin{itemize}
\tightlist
\item
  To help you develop and refine questions for your group project
\item
  To help you think through the various aspects of the project
\end{itemize}

\end{frame}

\begin{frame}{Four rules for QFT}
\protect\hypertarget{four-rules-for-qft}{}

\begin{enumerate}
\tightlist
\item
  Ask as many questions as you can
\item
  Do not stop to discuss, judge, or answer the questions
\item
  Write down every question exactly as it is stated
\item
  Change any statement into a question
\end{enumerate}

\end{frame}

\begin{frame}{Which of the above four rules is the hardest to follow?}
\protect\hypertarget{which-of-the-above-four-rules-is-the-hardest-to-follow}{}

\end{frame}

\begin{frame}{The prompt}
\protect\hypertarget{the-prompt}{}

\begin{itemize}
\tightlist
\item
  Pick a topic phrase for your group project if you have not already
  done so.
\item
  This can be:

  \begin{itemize}
  \tightlist
  \item
    The Green New Deal
  \item
    Solar Energy
  \item
    Water Safety
  \end{itemize}
\item
  Write down the ``prompt'' on your sheet
\end{itemize}

\end{frame}

\begin{frame}{The Question}
\protect\hypertarget{the-question}{}

Take five minutes, and put down your list of questions on the sheet

\end{frame}

\begin{frame}{Choose three questions that you find to be the most
interesting}
\protect\hypertarget{choose-three-questions-that-you-find-to-be-the-most-interesting}{}

Label them yellow and put a star in column A

\end{frame}

\begin{frame}{Type of Questions}
\protect\hypertarget{type-of-questions}{}

A question can be open-ended or close-ended

\begin{itemize}
\tightlist
\item
  Close-ended question

  \begin{itemize}
  \tightlist
  \item
    How much extra death does climate change cause to the Commonwealth
    of Massachusetts each year?
  \item
    Rigorous scientific hypothesis testing
  \end{itemize}
\item
  Open-ended question

  \begin{itemize}
  \tightlist
  \item
    What is the economic/societal impact of climate change to the
    Commonwealth of Massachusetts?
  \end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Label your question as close-ended or open-ended}
\protect\hypertarget{label-your-question-as-close-ended-or-open-ended}{}

\end{frame}

\begin{frame}{}
\protect\hypertarget{section-1}{}

A question can also be positive or normative:

\begin{itemize}
\tightlist
\item
  Positive questions: finding facts

  \begin{itemize}
  \tightlist
  \item
    How much extra death does climate change cause to the Commonwealth
    of Massachusetts each year?
  \item
    What is the economic/societal impact of climate change to the
    Commonwealth of Massachusetts?
  \end{itemize}
\item
  Normative questions: finding alternatives

  \begin{itemize}
  \tightlist
  \item
    Is moving vulnerable population out the BEST strategy for them to
    adapt to climate change?
  \item
    What is the best strategy to prepare vulnerable population for the
    upcoming climate challenge?
  \end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Label your question as positive or normative}
\protect\hypertarget{label-your-question-as-positive-or-normative}{}

\end{frame}

\begin{frame}{Take one of the questions, and try to improve the original
statement}
\protect\hypertarget{take-one-of-the-questions-and-try-to-improve-the-original-statement}{}

Put it underneath your list of questions.

\end{frame}

\begin{frame}{Towards the next steps}
\protect\hypertarget{towards-the-next-steps}{}

\begin{itemize}
\tightlist
\item
  What type of property right governs the good/service of your interest?
\item
  Who are the stakeholders
\item
  What are the trade-offs that are involved with your question?
\end{itemize}

\end{frame}
